### 2022-03-17 ms/PrestigeBias.tex
update

\clearpage
\bibliography{refs}
\bibliographystyle{apalike}
\end{document}

>>>>

\subsection{Prestige in medicine \citep{medical_prestige}}
So far we presented the existence of prestige in nature and in humans. We mostly discussed it in regard of social ranking in animals, and what are the costs and benefits. In humans, we mostly addressed spread of adaptive or maladaptive traits due to the prestige bias. \citet{medical_prestige} present a specific and important effect of prestige - its significance for medical specialties and diseases.
They examined literature from 1950 to 2005 regarding the effects of prestige on medicinal practices. They discovered that active, specialized, biomedical, and high-technological types of medicine on organs in the upper part of the bodies of young and middle-aged people were accorded high levels of prestige, while medicine with opposite characteristics had low levels of prestige. They have concluded that such differences in prestige bear consequences for actual priority setting in healthcare systems. They discovered that surgery counts as the most prestigious specialty, while psychiatry is the less prestigious. In addition, doctors tend to rank practices that require more time to master as more prestigious, while other procedures that are considered \textit{easier} are less prestigious. \citet{medical_prestige} found that the advance in technology and research was in accordance with the prestige rankings.
\clearpage
\bibliography{refs}
\bibliographystyle{apalike}
\end{document}
